### 2018-09-01 pilot_manuscript.Rmd
New MFD datasets!

```{r new_data, include = FALSE}
#take final$stemmed column loop over this

harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(harmstuffthing$words[harmstuffthing$words != "" & harmstuffthing$words != "NA"])]

@@

>>>>

```{r new_data, include = FALSE}
#take final$stemmed column loop over this
#Harm
harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA"])]

@@

#Fair
fair_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA"])]

#bind with original
fair_final_data = rbind(fair_final_data, temp2)
}

#Ingroup
ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA"])]

#bind with original
ingroup_final_data = rbind(ingroup_final_data, temp2)
}

#Authority
authority_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA"])]

#bind with original
authority_final_data = rbind(authority_final_data, temp2)
}

#Purity
purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA"])]

#bind with original
purity_final_data = rbind(purity_final_data, temp2)
}
